---
layout: page
permalink: "research/"
---
Scholary papers describing the methodology
========================================================

```{r setup, include = FALSE, cache = FALSE}
library("RefManageR")
bib <- ReadBib("TH.bib", check = FALSE)
BibOptions(check.entries = FALSE, style = "html",
           cite.style = "authoryear", bib.style = "numeric")
```
Transformation models have been around for more than 50 years, starting 
with the seminal paper introducing ``Box-Cox'' power-transformations
published by George Box and Sir David Cox in 1964. 
Later developments focused on a semiparametric understanding
of these models, most importantly the partial likelihood approach to
parameter estimation in the Cox proportional hazards model.

During the last decade, fully parametric versions of transformation models
have been studied. Model inference is much simpler once all components of
the models have been parameterised appropriately. Research on
transformation models implemented in the 
[mlt add-on package](https://CRAN.R-project.org/package=mlt) started with a
gradient-boosting algorithm for conditional transformation models
`r Citep(bib, "Hothorn_Kneib_Buehlmann_2014")`. This algorithm optimises the
Brier score for model estimation. It turned out that maximum likelihood
estimation is computationally and conceptionlly much simpler and also helps
to estimate models for discrete or censored data
`r Citep(bib, "Hothorn_Moest_Buehlmann_2017")`. So-called most likely
transformations are implemented in the
[mlt add-on package](https://CRAN.R-project.org/package=mlt)
`r Citep(bib, "Hothorn_2018_JSS")`.

A generalisation of binary logistic regression models to continuous outcomes
featuring parameters interpretable as log-odds ratios were described
in `r Cite(bib, "Lohse_Rohrmann_Faeh_2017")`. Simple transformation models
as well as more complex transformation models 
(for example transformation trees
and forests) for body mass index distributions are discussed in
`r Cite(bib, "Hothorn_2018")`. Two likelihood-based boosting methods for
transformation models are introduced in `r Cite(bib, "Hothorn_2019")`.

**References**

```{r results = "asis", echo = FALSE}
PrintBibliography(bib, .opts = list(check.entries = FALSE, sorting = "ynt"))
```

