---
layout: page
permalink: "software/"
---

A Simple Transformation Model
========================================================

```{r include=FALSE}
knitr::opts_chunk$set(fig.path='../images/')
```


First, install and fire-up R on your computer. Within R, one needs to
install the tram package by typing

```{r eval=FALSE}
install.packages("tram")
```

and hitting the ENTER key. The tram package implements simple formula-based
interfaces to some important transformation models. The models themself are
fitted using algorithms implemented in [mlt add-on
package](https://CRAN.R-project.org/package=mlt).

Once the package is installed, you can load it using

```{r results: hide}
library("tram")
```

Now all tram functions are ready to be used, for example the Colr()
function for fitting a series of potentially stratified logistic regression
models to a continuous outcome variable (let's start with median 
Boston Housing values):

```{r}
data("BostonHousing2", package = "mlbench")
library("survival")
BostonHousing2$y <- with(BostonHousing2, Surv(cmedv, cmedv < 50))
Colr_BH_1 <- Colr(y | 0 + chas ~ crim + zn + indus + nox + 
                  rm + age + dis + rad + tax + ptratio + b + lstat, 
                  data = BostonHousing2, support = c(10, 50))
summary(Colr_BH_1)
```
Two separate transformation function are fitted (for houses near and off
Charles river, variable chas). The remaining variables enter a linear
predictor those coefficients can be interpreted as log-odds ratios. Note
that median housing values larger than 50 are correctly treated as being 
right-censored in the likelihood-

The model can be used to extract the corresponding 
conditional distribution functions. Let's put the first house into two
locations, near and off Charles river. Then, we compute the two conditional
distribution functions:

```{r BHplot, fig.width=9, fig.height=6}
nd <- BostonHousing2[c(1, 1),]
nd$chas <- sort(unique(BostonHousing2$chas))
library("colorspace")
col <- diverge_hcl(2, h = c(246, 40), c = 96, l = c(65, 90))
plot(as.mlt(Colr_BH_1), newdata = nd, type = "distribution", col = col)
legend("bottomright", legend = c("Off", "Near"), title = "Charles river",
       col = col, lty = 1, bty = "n")
```
It appears that houses near the river are more expensive, and the
variability is also larger compared to houses far away from the river.

The most important feature in this model is that the shape of these
distributions have been estimated from data although the models are fully
parametric! An introduction to the underlying technology with many more
examples is available from
the [mlt.docreg package vignette](https://cran.r-project.org/web/packages/mlt.docreg/vignettes/mlt.pdf).
