---
layout: page
permalink: "/software/"
---

A Simple Transformation Model
========================================================

```{r include=FALSE}
knitr::opts_chunk$set(fig.path='../assets/img/')
```


First, install and fire-up R on your computer. Within R, one needs to
install the tram package by typing

```{r eval=FALSE}
install.packages("tram")
```

and hitting the ENTER key. Once the package is installed, you can
load it using

```{r results: hide}
library("tram")
```

Now all tram functions are ready to be used, for example the Colr()
function for fitting a series of potentially stratified logistic regression
models to a continuous outcome variable:

```{r}
data("BostonHousing2", package = "mlbench")
library("survival")
BostonHousing2$y <- with(BostonHousing2, Surv(cmedv, cmedv < 50))
Colr_BH_1 <- Colr(y | 0 + chas ~ crim + zn + indus + nox + 
                  rm + age + dis + rad + tax + ptratio + b + lstat, 
                  data = BostonHousing2)
summary(Colr_BH_1)
```
The model can be used to extract the corresponding 
conditional distribution functions

```{r fig.width=9, fig.height=6}
nd <- BostonHousing2[c(1, 1),]
nd$chas <- sort(unique(BostonHousing2$chas))
library("colorspace")
col <- diverge_hcl(2, h = c(246, 40), c = 96, l = c(65, 90))
plot(as.mlt(Colr_BH_1), newdata = nd, type = "distribution", col = col)
legend("bottomright", legend = levels(nd$chas), col = col, lty = 1, bty = "n")
```
